Fusion Moves for Correlation Clustering

### 2014-11-11 paper/introduction-old.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{eso-pic}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{placeins}

% Include other packages here, before hyperref.
\usepackage{my_macros}
\usepackage{paralist}
\usepackage{amsthm}
% \usepackage{dirtytalk} fah: my miktex didn't like this; and we don't need it here. 
%\usepackage{framed}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{setspace}
%for tikz
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}
\usepackage{filecontents}
%\usepackage{scrextend}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

\newcommand{\footlabel}[2]{%
    \addtocounter{footnote}{1}%
    \footnotetext[\thefootnote]{%
        \addtocounter{footnote}{-1}%
        \refstepcounter{footnote}\label{#1}%
        #2%
    }%
    $^{\ref{#1}}$%
}

\newcommand{\footref}[1]{%
    $^{\ref{#1}}$%
}
\usetikzlibrary{arrows,positioning,automata,shadows,fit,shapes}
\usetikzlibrary{arrows,petri,topaths}
\usetikzlibrary{positioning,fit,calc}
\usetikzlibrary{shapes.arrows,chains,decorations.pathreplacing,fadings}
\usetikzlibrary{calc, matrix, backgrounds}

%%%%%%global tikz styles

\tikzstyle{eBlack}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=black!70!black, font=\small,align=left, line width=1mm]
\tikzstyle{eNotCut}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=green!70!black, font=\small,align=left, line width=1mm]
\tikzstyle{eBlue}=[very thick,minimum size = 0.5cm,inner sep = 0pt,draw=blue!70!black, font=\small,align=left, line width=1mm]
\tikzstyle{eCut}=[very thick,dotted,minimum size = 0.5cm,inner sep = 0pt,draw=black, font=\small,align=left, draw=red!70!black, line width=1mm]

\pgfplotsset{every axis/.append style={
  every axis y label/.style = {at={(ticklabel cs:0.5)}, rotate=90, anchor=south},
  axis x line = {bottom},
  axis y line = {left},
  tick align = outside,
  ymajorgrids = true,
%  legend style = {draw=none, at={(1.05, 0.5)}, anchor=west, font=\small},
  legend style = {font=\tiny},
  legend columns = 1,
  every axis plot/.append style = {line width=1pt},
  label style = {font=\small},
  tick label style={font=\small},
  scaled ticks = false,
}}

% Two Colored Circle Split 
\makeatletter
\tikzset{circle split part fill/.style  args={#1,#2}{%
 alias=tmp@name, 
  postaction={%
    insert path={
     \pgfextra{% 
     \pgfpointdiff{\pgfpointanchor{\pgf@node@name}{center}}%
                  {\pgfpointanchor{\pgf@node@name}{east}}%            
     \pgfmathsetmacro\insiderad{\pgf@x}
      \fill[#1] (\pgf@node@name.base) ([xshift=-\pgflinewidth]\pgf@node@name.east) arc
                          (0:180:\insiderad-\pgflinewidth)--cycle;
      \fill[#2] (\pgf@node@name.base) ([xshift=\pgflinewidth]\pgf@node@name.west)  arc
                           (180:360:\insiderad-\pgflinewidth)--cycle;            
         }}}}}  
 \makeatother

%\usepackage{tkz-berge}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\definecolor{shadecolor}{rgb}{0.01,0.199,0.1}
\usepackage{xargs} 
\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage{bm}% ändert \boldsymbol
\def\arraystretch{0.8}
\renewcommand{\tabcolsep}{2pt}
\newcommand{\thickline}{2pt}
\newcommand{\scatterplotpath}{./scatterplots/}

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}
\newcommandx{\unsure}[2][1=]{\todo[linecolor=red,backgroundcolor=red!25,bordercolor=red,#1]{#2}}
\newcommandx{\change}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}
\newcommandx{\info}[2][1=]{\todo[linecolor=OliveGreen,backgroundcolor=OliveGreen!25,bordercolor=OliveGreen,#1]{#2}}
\newcommandx{\improvement}[2][1=]{\todo[linecolor=Plum,backgroundcolor=Plum!25,bordercolor=Plum,#1]{#2}}
\newcommandx{\thiswillnotshow}[2][1=]{\todo[disable,#1]{#2}}
\newcommand{\OR}{\textrm{ or }}

% \cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

\newcommand{\realplot}[1]{
\begin{tikzpicture}
    \begin{axis}
        \addlegendimage{empty legend}\addlegendentry{Matrix #1}
        \addplot {0};
        \addplot {1};
        \addplot {2};
        \addplot {3};
    \end{axis}
\end{tikzpicture}}

% \newcommand{\anytimeplot}[1]{
%   \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/knott-3d-300.data};              \addlegendentry{HC}
%   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data3/knott-3d-300.data};          \addlegendentry{HC-CGC}
%   \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/knott-3d-300.data};               \addlegendentry{CGC}
%   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/knott-3d-300.data};          \addlegendentry{KL}
%   \addplot[color=purple,mark=x] table[x=time, y=MCR-CCFDB]{data3/knott-3d-300.data};     \addlegendentry{MC-R}
%   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data3/knott-3d-300.data};       \addlegendentry{MC-I}
%   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
%   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-MC}
%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
% }
\newcommand{\anytimeplot}[1]{
  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/#1.data};              \addlegendentry{HC}
  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/#1.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/#1.data};               \addlegendentry{CGC}
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL} 
  \addplot[color=yellow!50!black,mark=square] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{CCFusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{CCFusion-HC-CGC}
  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{CCFusion-WS-MC}
  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{CCFusion-WS-CGC}
}
%  \addplot[color=yellow!50!black,mark=o] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
  %\addplot[color=green!50,mark=o] table[x=time, y=PIVOT*]{data3/#1.data};          \addlegendentry{PIVOT-BOEM}

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}
%%%%%%%%% TITLE
\include{my_macros.tex}
%\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}
\title{Fusion Moves for Correlation Clustering}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
  \color{red} \textbf{TODO:}
Correlation clustering, or multicut partitioning, is the NP-hard problem of partitioning an undirected graph or image with positive / attractive and negative / repulsive edge weights such that the sum of cut edge weights is minimized. We here present a move-making heuristic that uses cheaply generated proposal clusterings to iteratively and monotonously improve upon the best previously found clustering. A valid partitioning is maintained at all times, and solutions close to the global optimum are obtained faster than with any published technique.

%We address the problem of partitioning a  graph
%   into a previously unknown number of clusters.
%   Among all partitions, the one with the minimal 
%   sum of of cut edge weights is chosen. 
%   This problem is known as correlation clustering 
%   or multicut.
%   We propose a general framework to find
%   high quality approximate solutions for 
%   this NP-hard problem based on a move making algorithm:
%   We use candidate solutions from a proposal generator
%   to iteratively improve the best observed solution similar
%   to fusion moves.
%   The proposed solver outperforms any other solver
%   w.r.t. to any time performance.
%   The solutions found by this solver are close
%   to global optimal solutions w.r.t. energy
%   and problem specific measurements as VI for
%   image segmentation problems.

\end{abstract}
\section{Introduction}

Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010,Chen-2012}. Its value is, firstly, that it accommodates both positive / attractive \emph{and} negative / repulsive edge weights. Importantly, this allows doing justice to evidence in the data that two nodes or pixels do \emph{not} wish to end up in the same cluster or segment. This is in contrast to the submodular potentials so popularized by the graph cut algorithm, which only allow two nodes to be attracted to each other, or at most be agnostic about membership in the same cluster. Secondly, the algorithm does not require a specification of the number of clusters. This is in contrast to methods such as normalized cut \cite{} that can only accommodate attractive interactions and hence need the number of clusters to be specified.

\paragraph{Contribution.} The evident usefulness of correlation clustering and its clean and compact formulation in terms of an optimization problem, together with its unfortunate NP-hardness, are an invitation to develop fast approximate solvers. The basic idea of the move making algorithm proposed here is to maintain, at all times, a best current partitioning; and to iteratively improve it (as we show, monotonously) by considering diverse and cheaply generated proposal partitionings. Any two nodes that are in one cluster in both the current and the proposal partitioning are contracted. Edges to contracted nodes are equally combined and reweighted, and the correlation clustering problem is then solved on this reduced graph. We offer a polyhedral characterization of this strategy, and evaluate it in conjunction with two versatile proposal generators.   We conduct experiments on a broad range of data sets ranging from 2D and 3D segmentation problems to clustering in signed social networks. The results suggest that this simple move making algorithm is the fastest technique known today, reaching close to globally optimal solutions in a tenth or a hundredth of the time required by the most efficient exact solvers.

\paragraph{Related Work.}
A natural approach is to solve the integer linear programming problem directly. To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation. Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning. The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.

Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}. The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs. Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.

Finally, there are heuristic methods such as ...

---------------END OF SUGGESTION ----------------------------------

Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010} as a first step
towards understanding an image or data in general. 
The correlation clustering problem is the following:
Given an undirected edge weighted graph, 
where positive weights (\emph{attractive}) encourage the adjacent nodes to be in the same cluster
and negative weights (\emph{repulsive}) encourage the nodes to stay in different cluster, 
find the clustering of nodes such that the sum over weights of edges between clusters is minimized.
Note that this problem formulation does not included a predefined number of clusters.

@@

% \subsection{Karger-Stein Algorithms}
% Use randomized procedure to reduce the number of nodes / edges to a reasonable 
% number.
% On the smaller graph, more expensive solvers are used.

%\input{inputs/fig_hc_alg.tex}

\section{Energy Based Hierarchical Clustering}\label{sec:ehc}
Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation~\cite{arbelaez_2006}.
In each step, the edge with the highest weight $w$ is
contracted (red edges in Fig.~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
In agglomerative clustering, weights of
parallel edges are merged into single edges.
For image segmentation, the length
weighted mean is used to do this update~\cite{arbelaez_2006}.

While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
agglomeration with respect to our energy function.
For this we propose to use energy based agglomeration
withe the following update rule:
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
We call HC with this update method Energy base Hierarchical Clustering (EHC).

We stop EHC if the highest edge weight is
smaller or equal to zero  (green edge in Fig.~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

% Hierarchical clustering is fast, and 
% due to the agglomeration of edge weights, 
% {\color{red} hierarchical clustering is robust against noise}.
% {\color{yellow} [ First most similar nodes are merged...]
% In agglomerative clustering, weights of
% parallel edges are merged into single edges.}
% For image segmentation, the length
% weighted mean is used to do this update [ref].

% [We contrary on those works work directly on energy functions and that why ...]
% We propose to use Energy Based Hierarchical Clustering (EHC) to find
% solutions for correlation clustering.

% To make EHC follow the energy, we propose 
% the following update rule:
% Whenever there are multiple edges between 
% a pair of nodes, these edges are merged into a single edge
% by summing up their weights, since we 
% minimize the sum of the cut edges.
% The algorithm stops if the highest edge weight is
% smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
% contraction leads to worse energies.

Given the intrinsic greediness of hierarchical clustering, 
and the fact that EHC does only local decisions, it is 
sensitive against salt and paper noise 
and we do not expect very good solutions.

But EHC is very fast, and can be used to initialize
CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
is spend in the \emph{cut phase} to solve the 
first 2 coloring on the complete graph.
As shown in Sec.~\ref{sec:exp},
allowing CGC to start from the EHC solution
can improve performance drastically.

% Common cluster distances
% \begin{itemize}
% \item Single-Link: Nearest Neighbor - their closest members.
% \item Complete-Link: Furthest Neighbor - their furthest members.
% \item Centroid: Distance between centroids
% \item Group Average: average of all cross-cluster pairs.
% \end{itemize}

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}

Fusion moves as defined in \cite{Lempitsky-2010} work
in the node domain and do not work properly for 
objective functions as Eq.~\ref{eq:nodeproblem} since
the node coloring is ambiguous and has no semantic meaning (see Fig.~\ref{fig:fusion_abiguty}).
In the following, we propose a more suitable fusion move for correlation
clustering which works on the edge domain.
%
Given two proposal solutions $y'$ and $y''$,
$\mathcal{C}$ is the set of edges
which are uncut in $y'$ and $y''$.
%
\begin{align}
\breve{y}    & =  y' \cup y'' \\
\mathcal{C}  & =  \{ (i, j) \quad | \quad \breve{y}_{ij} = 0 \}
\end{align}
%
The fusion move for correlation clustering is solving Eq.~\ref{eq:edgeproblem}
with additional \emph{must-link constraints} for all edges in $\mathcal{C}$.
%
\begin{align}
  y^* &=& \argmin_{y \in P(G)} \sum_{ (i,j) \in E } w_{ij} \cdot y_{ij} \label{eq:fusion_move_a}.\\ 
  s.t & &  y_{ij} = 0 \quad \forall (i, j) \in \mathcal{C} \nonumber
\end{align}
%
By construction, solving Eq.~\ref{eq:fusion_move_a} cannot increase the energy:
\begin{align}
  \sum  w_{ij} \cdot y^*_{ij}  \leq \min \left( \sum  w_{ij} \cdot y'_{ij} ,  \sum   w_{ij} \cdot y''_{ij} \right)
\end{align}
%

Once we know how to fuse segmentations, the actual algorithm 
for correlation clustering 
is simple and similar to the fusion move algorithm of Lempitsky \etal~\cite{bagon_2011_arxiv}.
We iteratively improve the best solution by
fusing it with proposal solutions.
The inherent difference is how we define the fusion.
We fuse the segmentations according to Eq.~\ref{eq:fusion_move_a}.
%
How to optimize  Eq.~\ref{eq:fusion_move_a} in an more efficient way is
described in the following section.

\input{inputs/fig_fusion.tex}

%\textbf{old}
%
%Motivation Using Fusion moves -> problem ambiguity
%
%A consistent edge labeling $y$ defines a segmentation of $V$ by enumerating the connected components 
%in $G|_y=(V,\{e\in E|y_e=0\}$ by $l_v = \#(v)$, where $\#(v)$ denotes the number of the connected component of the %node $v\in V$.
%
%We define the contradiction of graph $G_y=(V_y,E_y)$
%with $V_y=\{\#(v)|v\in V\}$ and $E_y=\{\#(v),\#(u)|uv\in E, y_{uv}=1\})$.

%\input{inputs/fig_alg_graph.tex}

\subsection{Fast Optimization} \label{sec:fast_optimization}

Eq.~\ref{eq:fusion_move_a} can be solved efficiently, since 
we can work on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes.
This coarser graph is constructed by contracting all must-link edges
(see Fig.~\ref{fig:move_graph}).

TODO:
Here we need to proof that it is equivalent 
to optimize the contracted graph !

\input{inputs/fig_contraction.tex}
\input{inputs/fig_projection.tex}

\input{inputs/fig_move_graph.tex}

%-------------------------------------------------------------------------
%\subsection{Fusion Move Solver}

%-------------------------------------------------------------------------
\subsection{Proposal Generators}

As discussed in \cite{Lempitsky-2010}, proposals
should have two properties: \emph{quality} 
and \emph{diversity}.
The quality / energy of the individual proposals
ensures low energy solutions since the
result of the fusion cannot be higher then
the energy of the current best solution.
Diversity between the individual proposals
reduces the chances to get stuck in local minima.
For correlation clustering fusion we add a third
property: \emph{size}.
The size of the contraction graph directly
depends on the number of connected components
in the proposal solution and the current best solution.
The extreme  case is a proposal where each 
node is in a separate connnected component.
Solving the fusion move with such a proposal
is equivalent to solving the original problem.
Solving the fusion move with a proposal with 
a single connected component will result 
in the current best solution.
Therefore the size of the proposals
should be small enough, such that solving
eq.~\ref{eq:edgeproblem} can
be done fast enough, but large enough to make
meaningful moves (??? this last sentence needs to be rewritten).

%\begin{algorithm}
%    \begin{scriptsize}
%        \caption{Proposal Generators}\label{alg:proposal_gen}   
%        \begin{algorithmic}[1]
%            %\Require $J(x) \leq J(x')$
%            %\Ensure $J(\hat{x}) \leq J(x)$
%            %\vspace{0.3cm}
%            \Procedure{Rand2Coloring}{$x,G=(E,V),W$}
%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
%            \State $x'= \argmin\limits_{\bar{x}} \sum\limits_{e_{ij} \in E } \tilde{w}_{ij}[\bar{x}_i \neq \bar{x}_j]  [x_i = x_j]   $
%
%            $ \quad\quad s.t.\quad x_i \in \{0, 1\} \forall i $
%            \State \textbf{return} $x'$
%            \EndProcedure
%            %
%            %
%            \vspace{0.3cm}
%            \Procedure{RandEdgeWeightedWatersheds}{$x,G=(E,V),W$}
%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
%            \State $ getRandomSeeds$
%            \State $ runEdgeWeightedWs$
%            \EndProcedure   
%            %
%            %
%            \vspace{0.3cm}
%            \Procedure{RandHierarchicalClustering}{$x,G=(E,V),W$}
%            \State $\tilde{W} \gets \textbf{\scriptsize{randomize}}(W) $
%            \State $\hat{G}=(\hat{E},\hat{V}) \gets G=(E,V)$
%            \State $\hat{W} \gets W$
%            \While{$|\hat{V}|>\gamma$ \textbf{and}  $\max(\hat{W})>\theta$ }
%                \State $\hat{G}=(\hat{E},\hat{V}),\hat{W} \gets 
%                    \textbf{\scriptsize{contract}}(\hat{G},\hat{W},  \argmax\limits_{\hat{E}}(\hat{W}) )$
%            \EndWhile
%            \State $x' \gets \textbf{\scriptsize{getClusterResults}}(???) $ 
%            \EndProcedure
%        \end{algorithmic}
%    \end{scriptsize}
%\end{algorithm}

\noindent \textbf{Randomized HierarchicalClustering (RHC):}
%\subsubsection{Randomized HierarchicalClustering (RHC)}
%
To generate proposals cut we can use bottom up hierarchical clustering.
In each step we contract the edge with the highest weight.
Parallel edges are merged into single edges by summing their weights.
We stop when a certain number of nodes is reached, or the
largest edge weight among the not yet contracted edges is smaller then a certain threshold.
To get versatile proposals we either add noise 
to the edge weighs or permute a certain number of weights.

%\subsubsection{Randomized MaxCut  (RMC)}
%
%To get energy aware proposals we can use max cuts.
%The max cut objective is the same as
%the multicut objective, but only two 
%node colors are allowed.
%Therefore solutions of the max cut objective
%might be useful proposals.
%To create different proposals we set 
%the weight of edges which are cut 
%in the best solution to zero.
%In this way we favor solutions 
%different form the current best. 
%In addition we either add noise permute a certain number of weights.

\noindent \textbf{Randomized Watersheds (RWS):}
%\subsubsection{Randomized Watersheds (RWS)}
%
The edge weighted watershed algorithm \cite{meyer_2013}
with random seeds can be used to get 
cheap proposals. Instead of $n$ seeds distributed uniformly
over all nodes we use the following.
Draw $n/k$ random edges only the negative edges, 
and give the two nodes of each random edge different seeds.
Doing so, a random subset of negative edges is forced
to be cut within each proposal.
For additional randomness, noise can be added to
the edge weighs.

%\input{inputs/fig_hc.tex}

\subsection{Properties and Polyhedral Interpretation}
An alternative interpretation of our method is shown in Fig.~\ref{fig:polyheadral}.
In each iteration the current and proposed segmentation define an inner polyheadral 
approximation of the original multicut polytope. 
Optimizing over this polytope is the same problem as the original one, but much smaller.
Furthermore, the costs does not change and and improvement in the smaller polytope will 
be the same in the original graph.
The choice of the proposal defines the shape of the auxiliary polytope. 
In the given toy example, the first (red) polytope give a huge improvement, the second proposal
defines the blue polytope which does not lead to an improvement. 
The third proposal generates the green polytope that includes the global optimal solution.

This procedure is fundamental different to common polyhedral multicut methods~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv}, 
which tighten a outer relaxation of the multicut polytope and contrary to our method do not operate in the feasible domain.

\begin{figure}
\centering
\input{polytope-tikz.tex}
\caption{Each move can be interpreted as an optimization of an inner polyhedral optimization.
Each polyhedral approximation includes the current vertex. Starting with $y_0$ we optimize over the red polytope 
and find $y_1$ as optima. When optimize over the blue polytope we stay in $y_1$ as optima.
When optimizing over the green polytope we find $y_2$ which we will never leaf again or any polytope containing $y_2$. 
}
\label{fig:polyheadral}
\end{figure}

\begin{theorem}[Equivalence]
The optimal multicut $\bar{y}^*$ on the contracted graph $G_y$
is equivalent to the optimal multicut $y^*$ in the original graph $G$ 
with additional must link constraints ($y^* \leq y$).
%
\begin{proof}
Since $y^*$ fulfills all  must link constraints, we have  $y^*\cdot w = \rho^{-1}_y(y^*)\cdot \bar{w}$.
Consequently, $y^*\cdot w = \rho_y(\bar{y}) \cdot w$ and  $\rho^{-1}_y(y^*)\cdot \bar{w}= \bar{y}\cdot\bar{w}$.
\end{proof}
%
\end{theorem}

\begin{theorem}[Monotone]
Let $y'$ and $y''$ be two proposal solutions and  $y^*$ the optimal fused segmentation.
Than $y^*$  will never decrease the energy:
$y^* \cdot w \leq  \min( y'\cdot w,  y''\cdot w) $ 
%
\begin{proof}
The feasible set of the fusion move includes per definition  $y'$ and $y''$.
If $y'$ or $y''$ would have lower multicut cost than $y^*$, $y^*$ would not be optimal 
and that why not the propose segmentation of a fusion.
\end{proof}
%
\end{theorem}

%\begin{remark}[Fix-point (pointless to me)]
%Let $Y$ be the set of possible proposals, than
%$y'$ is a fix-point if $y'=\arg\max_{y\in P(G_{y'\OR y''})} y\cdot w$ for all $y''\in Y$
%\end{remark}

\begin{remark}[Optimality]
Let $y'$ be the current and $y''$ the proposed segmentation.
If the optimal solution $y^*$ lies in $P(G_{y' \OR y''})$ than a optimal fusion move will return $y^*$.
\end{remark}

\section{Experiments}\label{sec:exp}
In our experiments we compare to the following methods withpublic available implementation.

For \textbf{CGC}~\cite{beier_2014_cvpr} we used the public available implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}
of the Beier~\etal and for \textbf{KL}~\cite{Kernighan-1970} the implementation in OpenGM\footlabel{opengm-master}{\url{https://github.com/opengm/opengm}}.
For integer multicuts (\textbf{MC-I}) and relaxed multicuts (\textbf{MC-R})~\cite{kappes_2013_arxiv} we try the public available implementation in OpenGM\footref{opengm-master}
of Kappes~\etal. We realize that their implementation has some limitations on large problems and make the following modifications.
Firstly, we use \emph{index-min-heap}~\cite{Sedgewick-2011} within the shortest path search by the Dykstra algorithm - this gives a speed up for MC-R.
Secondly, we follow~\cite{kroeger_2012_eccv} and search for shortest paths and add those only if they are non-chordal instead of searching for the shortest non-chordal path
during the separation procedure. Fig.~\ref{fig:at:knott-450b} show the improvements with our modifications compared to the implementation in OpenGM for the knott-3d-450 dataset.
This procedure is one magnitude faster, but might cause a few extra outer iterations.
In~\cite{kroeger_2012_eccv}. this has been used for MC-I only. 
For MC-R this search procedure is not sufficient and need to be followed by a search for a shortest non-chordal paths.
From the field of data-mining we compare to the PIVOT-algorithm~\cite{Ailon-2008} followed by a round of BOEM~\cite{Gionis-2007} denoted by \textbf{PIVOT-BOEM}.
We use the public available code of Micha Elsner\footnote{\url{http://www.ling.ohio-state.edu/~melsner/resources/correlation-readme.html}}.
While this implementation uses full adjacency matrixes it does not scale as well as the algorithm can and therefor can not be applied on all datasets.
We also run classical fusion moves~\cite{Lempitsky-2010} (\textbf{Fusion}) and select distinct labels for the two candidate segmentations.

As reported in~\cite{beier_2014_cvpr}, CGC is faster and gives better energies then PlanarCC~\cite{yarkony_2012_eccv} and Expand \& Explore~\cite{bagon_2011_arxiv}.
Therefore we exclude those in our experiments.

We compare this methods to the following methods suggested in the present paper.
%
Energy Based Based Hierarchical Clustering (\textbf{EHC})
as described in sec.~\ref{sec:ehc}.
%
CGC warm started with the solution from EHC denoted by \textbf{EHC-CGC}.
%
The proposed correlation cluster fusion algorithm with EHC-based and watershed-based proposals
 and MC-I and CGC as subproblem solvers denoted by 
\textbf{fusionCC-HC-MC},
\textbf{-HC-CGC},
\textbf{-WS-MC}, and 
\textbf{-WS-CGC}, respectively.
We set the size of the proposals fix to $10\%$ of the original problem size
and the standard derivation of the random edge noise to $1.5$.

 \begin{figure}[t]
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
     height= 4cm, 
    restrict y to domain=-80000:1000,
   %   restrict x to domain=10:4000,
    xlabel = {runtime},
    xmin = 10,
    xmax = 4100,
    ymax = 0,
    ymin = -80000,
    legend to name = ledgendPositionMC,
    legend columns=4,
    width = 0.9\columnwidth,
    scaled ticks = false
    ] 
    \addplot[color=red,mark=x] table[x=time, y=MC-CCFDB-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-old}
    \addplot[color=orange,mark=o] table[x=time, y=MC-CCFDB-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-new}
    \addplot[color=blue,mark=x] table[x=time, y=MC-CCIFD-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-old}
    \addplot[color=cyan,mark=o] table[x=time, y=MC-CCIFD-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-new}

    \end{semilogxaxis}
    \end{tikzpicture}
  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPositionMC}
  \hypersetup{linkcolor = red}
  \end{center}
    \caption{Comparison of the Multicut implementation of OpenGM and 
    our modified implementation, which can deal better with large scale problems. 
    However, for large scale problems it still does not scale.}
    \label{fig:at:knott-450b}
  \end{figure}

All experiments were run on Intel Core i5-4570 CPUs
with 3.20 GHz, equipped with 32 GB of RAM.
In our evaluation we make not use of multiple threads.
The methods were stopped if they exceed 30 minutes at the next possible interrupt point.

\subsection{Parameter Choice for CCFusion}
Beside the choice of the proposal generator and fusion method CCFusion has some more parameters, which need to be set.
The most crucial one is the number of segments in the proposal. For HC we also have to set the noise which is use to generate diversity.
Fig.~\ref{fig:parameterchoice} shows a evaluation of the impact of this parameters for a single instance of knott-3d-450 averaged over several random seeds.
The runtime many depend on the number of clusters in the proposal (Fig.~\ref{fig:parameterchoice} left), which controls the size of the auxiliary move problems.
The level of noise has no major impact on the runtime.
The energy of the final solution improves with finer proposals since this increase the search-space of the moves.
Although the level of noise has to be large enough to generate diverse proposals but also not to large to generate proposals with low energy.
As shown in Fig.~\ref{fig:parameterchoice} right the useful parameter set is quite large. This allows us to use the same parameters for \emph{all}
experiments. However we would like to note, that in practice we can improve the performance by adjust these parameters for the specific problem setting.
%
%
\begin{figure}[th]
\centering
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-time2.pdf}}
\fbox{\includegraphics[width=0.45\columnwidth,trim=3.5cm 8cm 4.5cm 8cm,clip]{images/grid-value2.pdf}}
\caption{Empirical evaluation of the impact of noise used for proposal generation and proposal size.
  Proposals with many segments causes longer runtime. Noise seemed not to be a critical parameter but should be selected large enough.
}
\label{fig:parameterchoice}
\end{figure}

>>>>

\section{Introduction}
Correlation clustering~\cite{Bansal-2002} also known as the multicut problem~\cite{chopra_1993_mp} 
is a basic primitive in computer vision~\cite{andres_2011_iccv,kroeger_2012_eccv,yarkony_2012_eccv,alush_2013_simbad} and data mining~\cite{Chierichetti-2014,Arasu-2009,Sadikov-2010} as a first step
towards understanding an image or data in general. 
The correlation clustering problem is the following:
Given an undirected edge weighted graph, 
where positive weights (\emph{attractive}) encourage the adjacent nodes to be in the same cluster
and negative weights (\emph{repulsive}) encourage the nodes to stay in different cluster, 
find the clustering of nodes such that the sum over weights of edges between clusters is minimized.
Note that this problem formulation does not included a predefined number of clusters.

@@
